Comparing GA Part 2

### 2022-03-17 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I made a line graph that shows how the diffence between mean phenotypes of snakes and newts goes though cycles

@@

title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims 100000gen newt_deaths/Newt_pop_size last 100gen"
y_label="Mean_predation"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
```

@@

title="Space: Newt VS Snake Boxplot Phenotype"
subt="25sims dif last 1000gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

title="Space: Newt VS Snake Boxplot Phenotype"
subt="25sims dif last 100gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

>>>>

GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size

@@

title="Space: Newt VS Snake Boxplot Color=Mean_predation"
subt="25sims 100000gen newt_deaths/Newt_pop_size last 100gen"
y_label="Mean_predation"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(mean_predation), fill=group), color="black")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

title="Space: Newt VS Snake Mean_predation"
subt="Sim A 100000gen newt_deaths/Newt_pop_size "
y_label="Mean_predation"
x_label="Generation"
ggplot(GA_file_100[which(GA_file_100$sim=="A"), ]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_line(aes(x=gen, y=as.numeric(mean_predation)), color="black")+

  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
```

@@

title="Space: Snake-Newt Mean Phenotype Boxplot"
subt="25sims dif last 1000gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

title="Space: Snake-Newt Mean Phenotype Boxplot"
subt="25sims dif last 100gen"
y_label="dif"
x_label="Simulation"
ggplot(data_subset_small) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim), y=as.numeric(dif), fill=group), color="darkorchid4")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Newt_mean_Pheno), fill=group), color="darkred")+
  #geom_boxplot(aes(x=factor(sim), y=as.numeric(Snake_mean_Pheno), fill=group), color="steelblue")+
  theme(plot.title = element_text(size=5)) +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))

title="Space: Snake-Newt Mean Phenotype"
subt="Sim A 100000 gen newt_mean_pheno "
y_label="Mean_predation"
x_label="Generation"
ggplot(GA_file_100[which(GA_file_100$sim=="A"), ]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_line(aes(x=gen, y=as.numeric(dif)), color="darkorchid4")+
